Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2017-02-08 Manuscript/Manuscript_COD_decomp.Rmd
refactored cxode

COD.levels <- c("Cardiovascular", "Cancers", "Communicable", 
                "Non-communicable", "Injuries", "All other causes")
cod_decomp_results$COD <- factor(cod_decomp_results$COD, COD.levels)
age_cod_results$COD <- factor(age_cod_results$COD, COD.levels)
```

```{r add_Census_Region, echo=FALSE}
#note that the Census Region of the South is partitioned into two for better display.

BlackWhite_results$Census_Region <- "South"
BlackWhite_results$Census_Region[BlackWhite_results$state %in% c("Iowa", "Kansas", "Minnesota", "Missouri", 
                                                 "Nebraska", "North Dakota", "South Dakota", 
                                                 "Illinois", "Indiana", "Michigan", "Ohio", 
                                                 "Wisconsin")] <- "Midwest"

BlackWhite_results$Census_Region[BlackWhite_results$state %in% c("Connecticut", "Maine", "Massachusetts", 
                                                 "New Hampshire", "Rhode Island", "Vermont",
                                                 "New Jersey", "New York", "Pennsylvania")] <- "Northeast"

BlackWhite_results$Census_Region[BlackWhite_results$state %in% c("Arizona", "Colorado", "Idaho", "Montana", 
                                                 "Nevada", "New Mexico", "Utah", "Wyoming",
                                                 "Alaska", "California", "Hawaii", "Oregon",
                                                 "Washington")] <- "West"

BlackWhite_results$Census_Region[BlackWhite_results$state %in% c("Delaware", "Florida", "Georgia", "Maryland", 
                                                  "North Carolina", "South Carolina", 
                                                  "Virginia", "Washington DC", "West Virginia")] <- "South Atlantic"

BlackWhite_results$Census_Region[BlackWhite_results$state %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                  "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "South Central"

BlackWhite_results$Census_Region <- factor(BlackWhite_results$Census_Region, levels = c("West", "Midwest", "South Central", "South Atlantic", "Northeast"))
```

```{r add_Census_Division, ncol = 3, echo = F}
BlackWhite_results$Census_Division <- NA

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Connecticut", "Maine", "Massachusetts", 
                                                                   "New Hampshire", "Rhode Island", "Vermont")] <- "New England"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("New Jersey", "New York", "Pennsylvania")] <- "Mid-Atlantic"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Illinois", "Indiana", "Michigan", "Ohio", 
                                                                 "Wisconsin")] <- "East North Central"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Iowa", "Kansas", "Minnesota", "Missouri", 
                                                                 "Nebraska", "North Dakota", "South Dakota")] <- "West North Central"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Delaware", "Florida", "Georgia", "Maryland", 
                                                                 "North Carolina", "South Carolina", 
                                                                 "Virginia", "Washington DC", "West Virginia")] <- "South Atlantic"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee")] <- "East South Central"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "West South Central"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Arizona", "Colorado", "Idaho", "Montana", 
                                                                 "Nevada", "New Mexico", "Utah", "Wyoming")] <- "Mountain"

BlackWhite_results$Census_Division[BlackWhite_results$state %in% c("Alaska", "California", "Hawaii", "Oregon","Washington")] <- "Pacific"

BlackWhite_results$Census_Division <- factor(BlackWhite_results$Census_Division, levels = c("New England", "Mid-Atlantic", "East North Central", "West North Central", "South Atlantic", "East South Central", "West South Central", "Mountain", "Pacific"))

```{r addvar_State_abbreviation, echo=FALSE}
BlackWhite_results <- BlackWhite_results %>% mutate(stabbrs = factor(state,  
                                                                     labels = c("AL", "AZ", "AR", "CA",
                                                                                "CO", "CT", "DE", "FL",
                                                                                "GA", "IL", "IN", "IA",
                                                                                "KS", "KY", "LA", "MD",
                                                                                "MA", "MI", "MN", "MS",
                                                                                "MO", "NE", "NV", "NJ", 
                                                                                "NM", "NY", "NC", "OH", 
                                                                                "OK", "OR", "PA", "RI", 
                                                                                "SC", "TN", "TX", "VA", 
                                                                                "WA", "DC", "WV", "WI")))

                                      # labels = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "DC",
                                      #            "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", 
                                      #            "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", 
                                      #            "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", 
                                      #            "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", 
                                      #            "VT", "VA", "WA", "WV", "WI", "WY")))

>>>>

COD.levels <- c("Cardiovascular", "Cancers", "Communicable", 
                "Non-communicable", "Injuries", "All other causes")

cod_decomp_results$COD <- factor(cod_decomp_results$COD, COD.levels)
age_cod_results$COD <- factor(age_cod_results$COD, COD.levels)
```

```{r add_Census_Variables, echo = F}
BlackWhite_results <- add_Census_Region(BlackWhite_results, state)
BlackWhite_results <- add_Census_Division(BlackWhite_results, state)
BlackWhite_results$stabbrs <- state.abb[match(BlackWhite_results$state, state.name)]
